---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Coverage Status](http://img.shields.io/codecov/c/github/gzt/teatimer/master.svg)](https://codecov.io/github/gzt/teatimer?branch=master) 
[![Travis-CI Build Status](https://travis-ci.org/gzt/teatimer.svg?branch=master)](https://travis-ci.org/gzt/teatimer) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/gzt/teatimer?branch=master&svg=true)](https://ci.appveyor.com/project/gzt/teatimer)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/teatimer)](https://cran.r-project.org/package=teatimer)



# teatimer

The goal of teatimer is to set an easy (albeit rough) timer. It has one function: `teatimer` which runs
`beepr::beep()` after however many minutes or seconds the user specifies. 
Be forewarned: because this runs using `Sys.sleep()`, it is not running in the background - the R console will 
not be available while it is running. Plan accordingly.


## Example

Here is a basic example of all the options: 

```{r example, eval=FALSE}
teatimer(time = 0, minutes = TRUE, sound = 1)
```

This immediately plays a 'ping' sound. The `minutes` argument, by default `TRUE`, indicates whether to treat the 
`time` argument as minutes (`TRUE`) or seconds (`FALSE`). The `sound` argument is passed to `beepr::beep()`. 
By default, it plays the 'ping' sound. To play a random sound, set `sound = 0`.


# Installation

teatimer is not currently available on CRAN, but you can install it with:

``` r
# install.packages("devtools")
devtools::install_github("gzt/teatimer")
```



Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

